{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-04-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

    \todo{
        This is just pseudo text. This is just pseudo text. 
        This is just pseudo text. This is just pseudo text \cite{necoara_linear_2019}. 

@@

    % BREGMAN DIV DEFINITION ===================================================================================

@@

            \begin{definition}[Strong convexity]\label{def:necoara-scnvx}

@@

            % DEFINITION OF WEAKER STRONG CONVEXITY ====================================================================
            \begin{definition}[Relaxations of Strong convexity]\label{def:necoara-weaker-scnvx}

@@

@@

                    Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 

@@

                    Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 

@@

        \subsection{Major Results in the paper}

@@

            % THEOREM | Q-SCNVX IMPLIES QUA ============================================================================
            \begin{theorem}(Q-SCNVX implies QUA)\label{thm:qscnvx-means-qua}

@@

                The projectin property remains true for nonconvex $X^+$, however the base case require rethinking. 

@@

            % THEOREM | QGG IMPLIES QUA ================================================================================

@@

            % THEOREM | QFC IMPLIES QGG  ===============================================================================

@@

            % THEOREM | SUFFICIENCY OF QFG =============================================================================

@@

            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} in our context because it will be used in later proofs. 
            In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
            In this case $\mu_g = 0$ and assuming $f$ is convex we have only $\mu_f = 0$. 
            Therefore the theorem specializes into the following inequality.

            \par
            The following theorems are about the relation between PEB and QFG. 
            \begin{theorem}[equivalence between QFG and PEB]

@@

>>>>

@@

    % ===================================================================================
    % BREGMAN DIV DEFINITION 
    % ===================================================================================

@@

            \begin{definition}[strong convexity]\label{def:necoara-scnvx}

@@

            %===================================================================
            % DEFINITION OF WEAKER STRONG CONVEXITY 
            % ==================================================================
            \begin{definition}[relaxations of strong convexity]\;\\

@@

                \label{def:necoara-weaker-scnvx}

@@

                    Denoted by $\mathbb S'(L_f, \kappa_f, X)$. 

@@

                    Denoted by $\mathbb U(L_f, \kappa_f, X)$. 

@@

        \subsection{Weaker conditions of strong convexity}

@@

            % ============================================================================
            % THEOREM | Q-SCNVX IMPLIES QUA 
            % ============================================================================
            \begin{theorem}[Q-SCNVX implies QUA]\label{thm:qscnvx-means-qua}

@@

                The projection property remains true for nonconvex $X^+$, however the base case require rethinking. 

@@

            % ================================================================================
            % THEOREM | QGG IMPLIES QUA 
            % ================================================================================

@@

            % ===============================================================================
            % THEOREM | QFC IMPLIES QGG  
            % ===============================================================================

@@

            % =============================================================================
            % THEOREM | SUFFICIENCY OF QFG 
            % =============================================================================

@@

            Before we start, we will specialize Theorem \ref{theorem:pg-ineq} because it will be used in later proofs. 
            In Assumption \ref{ass:necoara-2019-settings}, it can be seemed as taking $F = f + g$ in Assumption \ref{ass:smooth-add-nonsmooth} with $g = \delta_{X}$. 
            This makes $\mu_g = 0$ and assuming $f$ is convex we have $\mu_f = 0$. 
            Let $\beta = L_f$, and $x^+ = \Pi_{X}(x - L_f^{-1}\nabla f(x))$, it has for all $z \in X$: 
            \begin{align}\label{ineq:proj-grad}
                \begin{split}
                    f(z) - f(x^+) + \frac{L_f}{2}\Vert z - x\Vert^2
                    - \frac{L_f}{2}\Vert z - x^+\Vert^2
                    f(z) - f(x^+) + L_f\langle z - x^+, x^+ - x\rangle
                    + \frac{L_f}{2}\Vert x - x^+\Vert^2. 
                \end{split}
            Take note that when $z = x$ it has 
            \begin{align}\label{ineq:proj-grad2}
                0 &\le f(x) - f(x^+) - \frac{L_f}{2}\Vert x - x^+\Vert^2. 
            \par
            The following theorems are about the relation between PEB and QFG.
            % ==========================================
            % THEOREM | EQUIVALENCE BETWEEN QFG AND PEB 
            % ==========================================
            \begin{theorem}[equivalence between QFG and PEB]
                If $f$ is convex and satisfies Assumption \ref{ass:necoara-2019-settings}. 
                Then we have: 
                    \mathbb E(L_f, \kappa_f, X) &\subseteq \mathbb F(L_f, \kappa^2/L_f, X), 
                    \mathbb F(L_f, \kappa_f) 
                    &\subseteq 
                    \mathbb E\left(
                        L_f,
                        \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}, 
                        X
                    \right). 

@@

                \textbf{Firstly, we show that PEB implies QFG.}
                For any $x \in X$, define the gradient projection steps by $x^+ = \Pi_{X}(x - L^{-1}_f\nabla f(x))$. 
                Denote $\bar x^+_\Pi = \Pi_{X^+}x^+$. 
                Using \eqref{ineq:proj-grad} with $z = \bar x^+_\Pi$ it yields: 
                {\small
                    0 &\ge 
                    f(x^+) - f(x^+_\Pi) - L_f\langle x_\Pi^+ - x^+, x^+ - x\rangle
                    - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert^2
                    \quad&\ge 
                    \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
                    - \Vert L_f(x - x^+)\Vert\Vert x^+_\Pi - x^+\Vert
                    - \frac{1}{2L_f}\Vert L_f(x - x^+)\Vert^2   &\text{QFG, Cauchy}
                    &= \frac{\kappa_f}{2}\Vert x^+ - x_\Pi^+\Vert^2
                    - \frac{1}{2L_f}\left(
                        \Vert L_f(x - x^+)\Vert^2
                        + L_f\Vert L_f(x - x^+)\Vert\Vert x_\Pi^+ - x^+\Vert
                    \frac{\kappa_f + L_f}{2}\Vert x^+ - x^+_\Pi\Vert^2
                    - \frac{1}{2L_f}\left(
                        \Vert L_f(x - x^+)\Vert + L_f\Vert x - x_\Pi^+\Vert
                    \right)^2
                From the last line, by positivity of norm it has
                    \Vert L_f(x - x^+)\Vert + L_f\Vert x^+ - x_\Pi^+\Vert
                    &\ge \sqrt{L_f(\kappa_f + L_f)}\Vert x^+ - x^+_\Pi\Vert
                    \Vert L_f(x - x^+)\Vert
                    \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\Vert x^+ - x^+_\Pi\Vert. 
                Using property of projection onto $X$ we have 
                    \Vert x - \bar x\Vert &\le \Vert x - x_\Pi^+\Vert
                    \le \Vert x - x^+\Vert + \Vert x^+ - x^+_\Pi\Vert
                    &= \frac{1}{L_f}\Vert L_f(x - x^+)\Vert + \Vert x^+ - x^+_\Pi\Vert
                    \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert
                    \Vert x^+ - x^+_\Pi\Vert. 
                Combining the two above inequalities gives 
                {\small
                    \Vert L_f(x - x^+)\Vert
                    -
                    \left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right)\left(
                        \Vert x - \bar x\Vert - \frac{1}{L_f}\Vert L_f(x - x^+)\Vert
                    - \left(
                        \sqrt{L_f(\kappa_f + L_f)} - L_f
                    \right)\Vert x - \bar x\Vert
                        L^{-1}_f\left(\sqrt{L_f(\kappa_f + L_f)} - L_f\right) + 1
                    \right)\Vert L_f(x - x^+)\Vert
                    -\left(
                        \sqrt{L_f(\kappa_f + L_f)} - L_f
                    \right)\Vert x - \bar x\Vert
                    \sqrt{L_f(\kappa_f + L_f)}
                    \Vert L_f(x - x^+)\Vert
                    \iff&
                    \frac{\sqrt{L_f(\kappa_f + L_f)} - L_f}{\sqrt{L_f(\kappa_f + L_f)}}
                    \Vert x - \bar x\Vert 
                    \le
                    \Vert \mathcal G_{L_f}x\Vert. 
                Skipping algebra, the fraction simplifies to 
                    \frac{\kappa_f}{\kappa_f/L_f + 1 + \sqrt{\kappa_k/L_f + 1}}. 
                This gives PEB condition. 
                \textbf{We now show QFG implies PEB}. 
                From the error bound condition using $\kappa_f$ it has
                    \kappa_f^2\Vert x - \bar x\Vert^2
                    \le \Vert \mathcal G_{L_f}(x)\Vert^2
                    \underset{\eqref{ineq:proj-grad2}}{\le }
                    2L_f(f(x) - f(x^+)) \le 2L_f(f(x) - f^+). 
            \par
            The following theorem summarizes the hierarchy of the conditions listed in Definition \ref{def:necoara-weaker-scnvx}. 
            \begin{theorem}[Hierarchy of weaker S-CNVX conditions]\label{thm:weaker-scnvx-hierarchy}
                Let $f$ satisfy Assumption \ref{ass:necoara-2019-settings}, assuming convexity then the following relations are true: 
                    \mathbb S(\kappa_f, L_f, X) 
                    \subseteq \mathbb S'(\kappa_f, L_f, X)
                    \subseteq \mathbb G(\kappa_f, L_f, X) 
                    \subseteq \mathbb U(\kappa_f, L_f, X) 
                    \subseteq \mathbb F(\kappa_f, L_f, X). 

            \end{proof}
            \begin{remark}
                It's Theorem 4 in Necoara et al. \cite{necoara_linear_2019}.
            \end{remark}
        \subsection{Hoffman error bound and Q-SCNVX}

        \subsection{Feasible descent and accelerated feasible descent}

        \subsection{Application, KKT of linear programming}
